---
title: "p8105_hw5_xl3141"
author: "Xinyuan Liu"
date: "11/16/2021"
output: github_document
---
## Set up

```{r}
library(tidyverse)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

```{r}
homocide_df =
  read_csv("data-homicides-master/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")

homocide_df %>% 
  count(city_state, resolution)
```

let's focus on Baltimore

```{r}
baltimore_df =
  homocide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary =
  baltimore_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
  )

baltimore_test %>% 
  broom::tidy() %>% 
  select(estimate, contains("conf"))
```

function

```{r}
prop_test_function = function(city_df){
  
  city_summary =
    city_df %>% 
      summarize(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  
  return(city_test)
}

prop_test_function(baltimore_df)

```

iterate across all cities

```{r}
result_df =
  homocide_df%>% 
    nest(data = uid:resolution) %>% 
    mutate(
      test_results = map(data, prop_test_function),
      tidy_results = map(test_results, broom::tidy)
    ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, contains("conf"))

```

plot of estimate and confidence interval

```{r}
result_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

data import and tidying

```{r}
files = list.files("data/")

output = vector("list", length = 20)

for(i in 1:20) {
  
  output[[i]] = str_c("data/", files[[i]])
}

csv_import = function(path){
  
  data = read_csv(path)
  
  return(data)
}

participant_df =
  tibble(
    files = list.files("data/"),
    csv_import(output)
  ) %>% 
  mutate(
    files = str_replace(files, ".csv$", ""),
    files = str_replace(files, "con", "control"),
    files = str_replace(files, "exp", "experiment"),
    arm = files,
    arm = str_replace(arm, "_[0-1][0-9]$", "")
  ) %>% 
  rename(arm_id = files) %>% 
  relocate(arm)

```

plot

```{r}
participant_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "score"
  ) %>% 
  ggplot(aes(x = week, y = score, color = arm_id, group = arm_id)) + ## note: we need the group to be the same for lines
  geom_point() +
  geom_line() +
  facet_grid(. ~ arm)+
  labs(
    x = "week number",
    y = "observed score",
    title = "observed score across time"
  )
  
```

The plot above shows the observations on each subject over time. In general, individuals in the control group don't have significant change on their score across 8 weeks while individuals from the experiment group seems to have an increase in the score across 8-week-time-period.

## Problem 3

```{r}

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))%>% 
  janitor::clean_names()
  
```

write a function

```{r}

fill_in_function = function(x){
  
  if(is.numeric(x)){
    
    replace(x, is.na(x), mean(x, na.rm = TRUE))
    
  }
  else if(is.character(x)){
    
    replace(x, is.na(x), "virginica")
    
  }
}

new_df = map_df(iris_with_missing, fill_in_function)


```
